\begin{resume}

  \section*{发表的学术论文} % 发表的和录用的合在一起

  \begin{enumerate}[{[}1{]}]
  \addtolength{\itemsep}{-.36\baselineskip}%缩小条目之间的间距，下面类似
  
   \item X. C. Wu, J. Zhu(Corresponding), D. Y. Xiao, X. Q. Lin and R. Ding. GA-ADE: a novel approach based on graph algorithm to improves the detection of adverse drug events[J]. Multimedia Tools and Applications, 2017(11):1-15. (SCI,中科院三区)
   \item X. C. Wu, J. Zhu(Corresponding), Y. Tang, R. Ding, X. Q. Lin and C. H. Xu . MASM:A Novel Movie Analysis System based on Microblog. APWEB 2016:533-536 (CCF C类会议)
   \item J Zhu(Corresponding), X. C. Wu, X. Q. Lin, C. Q. Huang, G. Fung and Y. Tang. A novel multiple layers name disambiguation framework for digital libraries using dynamic clustering[J]. Scientometrics, 2018, 114(3):1-14. (SCI,中科院二区)
   \item J. Zhu, X. C. Wu, J. Xiao(Corresponding), C. Q. Huang, Y. Tang and K. Deng . Improved expert selection model for forex trading[J]. Frontiers of Computer Science, 2017(2):1-10. (SCI,中科院四区)
   \item J. Zhu(Corresponding), X. C. Wu, X. Q. Lin, D. Y. Xiao, J. Xiao, J. Huang and C. B. He. A self-learning graph clustering approach for protein complexes detection[J]. Control Theory and Applications, 2017. (EI期刊)
   \item Fen Yang, Jia Zhu(Corresponding), Xuming Wang, Xingcheng Wu, Yong Tang
	and Long Luo. A Multi-model Fusion Framework based on Deep Learning for
	Sentiment Classification.  CSCWD 2018(CCF C类会议)
  \end{enumerate}

  \section*{研究成果} % 有就写，没有就删除
  \begin{enumerate}[{[}1{]}]
  \addtolength{\itemsep}{-.36\baselineskip}%
  
    \item 软件著作. 学者日历软件V1.00(2016SR002107). 王大豪，汤庸，武兴成，曾伟铨，陈凌潇 2016.01
    \item 软件著作. 私人健康小助手软件(2016SR189032). 许传华，朱佳，武兴成，林雪琴，韦经敏，肖丹阳 2016.07
    \item 软件著作. 非冗余二手房信息平台(2016SR263089). 朱佳，李威，许传华，武兴成，陈凌潇，丁蕊 2016.10

  \end{enumerate}
\end{resume}
